Automatic Bicycle Balance Assistance Reduces Probability of Falling at Low Speeds When Subjected to Handlebar Perturbations\\Version 2.dev

### 2024-09-19 main.tex
Make R figures black and white and better size and legend.

Turning the balance-assist system on significantly \((p<0.05)\) reduces the
odds that a perturbation results in a fall while cycling at a speed of
6~\si{\kph}. Figure~\ref{fig:probability-6kph} visualizes the probability of
falling as a function of the mean and centered angular impulse per participant
for the balance assist state on and off while keeping all other explanatory
factors at their centered mean values. This figure is created by setting all
explanatory variables to there mean and calculating the probability from
Eq~\ref{eq:log-regress} for only change in angular impulse given the estimates
in Table~\ref{tab:freq-coefs-6}. The table indicates that the balance-assist
system halves (0.53) the odds that a perturbation results in a fall. This
figure shows that for relatively large impulses the probability to fall is
unity for both states of balance assist on and off. And for relatively small
impulses the probability to fall is null for both states. But for impulses in
the magnitude region (-1 to 0.5 STD), i.e. around the mean-centered fall
threshold, the probability of falling is significantly lowered with the balance
assist system on. The skewness of the probability curves arrives from the
interaction effects.\todo{check this statement about skewedness this and think
about it} Figure~\ref{fig:probability-10kph} shows the same result for the
10~\si{\kph} trials which has a similar trend of reducing the probability to
fall with the balance assist system turned on, but the effect is not
significant.
%
\begin{figure}
  \centering
  % NOTE : We could uncomment the longer subcaption if titles removed from
  % figures. It is currently redundant.
  \subcaptionbox{%Fall probability for the 6~\si{\kph} trials.
    \label{fig:probability-6kph}}{
    \includegraphics[width=120mm]{figures/predicted_fall_probability_6kmh.png}
  }
  \subcaptionbox{%Fall probability for the 10~\si{\kph} trials.
    \label{fig:probability-10kph}}{
    \includegraphics[width=120mm]{figures/predicted_fall_probability_10kmh.png}
  }
  \caption{Comparison of predicted fall probability for balance-assist on
    (blue) or off (red) when all other predictor variables are fixed at zero,
    except for the interaction effect between the balance-assist and the
    angular impulse. The ordinate axis is standard deviation around the mean
    (all perturbations), centered per participant.}
  \label{fig:probability}
\end{figure}

>>>>

Turning the balance-assist system on significantly \((p<0.05)\) reduces the
odds that a perturbation results in a fall while cycling at a speed of
6~\si{\kph}. Figure~\ref{fig:probability-6kph} visualizes the probability of
falling as a function of the mean and centered angular impulse per participant
for the balance assist state on and off while keeping all other explanatory
factors at their centered mean values. This figure is created by setting all
explanatory variables to there mean and calculating the probability from
Eq~\ref{eq:log-regress} for only change in angular impulse given the estimates
in Table~\ref{tab:freq-coefs-6}. The table indicates that the balance-assist
system halves (0.53) the odds that a perturbation results in a fall. This
figure shows that for relatively large impulses the probability to fall is
unity for both states of balance assist on and off. And for relatively small
impulses the probability to fall is null for both states. But for impulses in
the magnitude region (-1 to 0.5 STD), i.e. around the mean-centered fall
threshold, the probability of falling is significantly lowered with the balance
assist system on. The skewness of the probability curves arrives from the
interaction effects.\todo{check this statement about skewedness this and think
about it} Figure~\ref{fig:probability-10kph} shows the same result for the
10~\si{\kph} trials which has a similar trend of reducing the probability to
fall with the balance assist system turned on, but the effect is not
significant.
%
\begin{figure}
  \centering
  % NOTE : We could uncomment the longer subcaption if titles removed from
  % figures. It is currently redundant.
  \subcaptionbox{%Fall probability for the 6~\si{\kph} trials.
    \label{fig:probability-6kph}}{
    \includegraphics[width=80mm]{figures/predicted_fall_probability_6kmh.png}
  }
  \subcaptionbox{%Fall probability for the 10~\si{\kph} trials.
    \label{fig:probability-10kph}}{
    \includegraphics[width=80mm]{figures/predicted_fall_probability_10kmh.png}
  }
  \caption{Comparison of predicted fall probability for balance-assist on
    (blue) or off (red) when all other predictor variables are fixed at zero,
    except for the interaction effect between the balance-assist and the
    angular impulse. The ordinate axis is standard deviation around the mean
    (all perturbations), centered per participant.}
  \label{fig:probability}
\end{figure}
